### 2022-04-30 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_betacov_mapping@a58f35f21758c1dd7d0ce50ff5ef6ef8a368bfd2 🚀

\begin{figure}
\hypertarget{fig:compound}{%
\centering
\includegraphics{figures/risk_compounded.png}
\caption{Overlap of the percent of each pixel occupied by urbanized
structures, representing the degree of settlement, on the risk map.
Darker pixels correspond to more risk, in that the GMTC-derived risk of
fig.~\ref{fig:risk} is high \emph{and} the pixel is densely occupied by
human populations. This approach increases the relative risk of several
regions in Africa, and concenreates highlights the risk in India,
southeast China, and the arabic peninsula.}\label{fig:compound}
}
\end{figure}

>>>>

\begin{figure}
\hypertarget{fig:compound}{%
\centering
\includegraphics{figures/risk_compounded.png}
\caption{Overlap of the percent of each pixel occupied by urbanized
structures, representing the degree of settlement, on the risk map.
Darker pixels correspond to more risk, in that the GMTC-derived risk of
fig.~\ref{fig:risk} is high \emph{and} the pixel is densely occupied by
human populations. This approach increases the relative risk of several
regions in Africa, and highlights the risk in India, southeast China,
and the arabic peninsula where areas of high to moderate risk overlap
with areas of denser population.}\label{fig:compound}
}
\end{figure}
